---
title: "Poverty by Age and Sex"
author: "Amanda E. Ljuba"
date: '2022-06-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
read_excel("povertybyageandsexnewss.xlsx", 
    sheet = "Data")
poverty_as <- read_excel("povertybyageandsexnewss.xlsx", 
    sheet = "Data")
```

```{r}
subset_poverty_as <- poverty_as[3:28, 1:4]
subset_poverty_as
#subset_poverty_as$Estimate[1:26]
povas_pop <- subset_poverty_as$Estimate
povas_pop <- as.numeric(povas_pop)
povas_cat <- subset_poverty_as$Label
```


ggplot(subset_poverty_as, aes(x=povas_cat,y=povas_pop,fill=Sex)) + 
  geom_bar(stat = "identity",position=position_dodge(),width=.6)   + coord_flip() + theme(axis.text.x=element_text(angle=90)) +scale_fill_manual(values=c("tomato2", "darkblue"))+labs(title="Poverty by Age and Sex in Sterling, VA",subtitle="2020",caption= "Source: ACS data 2016-2020",x="Age",y="Estimated Population") +scale_x_discrete(limits=c("Under 5 years", "5 years","6 to 11 years","12 to 14 years","15 years","16 to 17 years","18 to 24 years","25 to 34 years","35 to 44 years","45 to 54 years","55 to 64 years","65 to 74 years","75 years and older")) 


```{r}
ggplot(subset_poverty_as,aes(x=povas_cat,y=povas_pop, fill=Sex))+geom_col(position="dodge",width=1.5)+theme(axis.text.x=element_text(angle=90, size=7.5, face="bold"))+ coord_flip()+scale_x_discrete(limits=povas_cat[1:length(povas_cat)/2])+labs(title="Poverty by Age and Sex in Sterling, VA 2020",subtitle="Income in the past 12 months below poverty level",caption= "Source: B17001 ACS data 2016-2020",x="Age",y="Estimated Population") 
```
Within the Sterling CPD, females ages 18 to 24 years old face the highest level of poverty by sex and age overall followed by females ages 35 to 44 years old and males ages 25 to 34 years old. The ACS lacks data on males 12 to 14, 15, and 34 to 44 years as well as females ages 16 to 17 years. From the data that is available, females tend to have higher levels of poverty than males especially from years 6 to 11. 
