---
title: "Updated Block Groups"
author: "NDP"
date: '2022-06-14'
output: html_document
editor_options: 
  chunk_output_type: console
---



* Number of teachers by schools based on the school websites
    * Sterling Elementary - 81 staff members; 32 teachers
    * Sugarland Elementary - 74 staff members; 52 teachers
    * Rolling Ridge Elementary - 93 staff members; 66 teachers
    * Forest Grove Elementary - 75 staff members; 55 teachers
    * Guilford Elementary - 88 staff members; 59 teachers
    * Sully Elementary - 54 staff members; 35 teachers???

#Staff Members vs Teachers    
```{r}
library(plotly)

Schools <- c("Sterling", "Sugarland", "Rolling Ridge", "Forest Grove", "Guilford", "Sully")
Teachers <- c(32, 52, 66, 55, 59, 35)
Staff <- c(49, 22, 27, 20, 29, 19)
dataSTAFF <- data.frame(Schools, Teachers, Staff)

figSTM <- plot_ly(dataSTAFF, x = ~Schools, y = ~Teachers, type = 'bar', name = 'Teachers', marker = list(color = 'rgb(255, 2, 2 )'))
figSTM <- figSTM %>% add_trace(y = ~Staff, name = 'Staff', marker = list(color = 'rgb(20, 252, 241 )'))
figSTM <- figSTM %>% layout(yaxis = list(title = 'Total Number'), barmode = 'stack')

figSTM
```

#Number of Staff Members by schools based on the school websites    
```{r}
labelsSTAFF = c("Sterling", "Sugarland", "Rolling Ridge", "Forest Grove", "Guilford", "Sully")
valuesSTAFF = c(81, 74, 93, 75, 88, 54)

figSTAFF <- plot_ly(type='pie', labels=labelsSTAFF, values=valuesSTAFF, 
               textinfo='label+percent',
               insidetextorientation='radial') %>% layout(title ='Staff Percentage', legend=list(title=list(text='Elementary Schools')))

figSTAFF
```
    
#Number of Teachers by schools based on the school websites    
```{r}
library(plotly)

labelsT = c("Sterling", "Sugarland", "Rolling Ridge", "Forest Grove", "Guilford", "Sully")
valuesT = c(32, 52, 66, 55, 59, 35)

figT <- plot_ly(type='pie', labels=labelsT, values=valuesT, 
               textinfo='label+percent',
               insidetextorientation='radial') %>% layout(title ='Teacher Percentage', legend=list(title=list(text='Elementary Schools')))

figT
```
    
    
```{r}
library(shiny)
library(shinythemes)
library(shinyjs)
library(ggplot2)
library(maps)
library(plotly)
library(DT)
library(dplyr)
library(tigris)
library(tidyverse)
library(tidycensus)
library(readxl)
library(collapsibleTree)
library(shinycssloaders)
library(leaflet)
library(leaflet.extras)
library(rvest)
library(sf)
library(shinydashboard)
library(shinydashboardPlus)
library(tidygeocoder)
library(janitor)
library(dplyr)
library(ggplot2)
library(magrittr)
options(tigris_use_cache = TRUE)

library(rstudioapi)
```

```{r set_up_API, }
readRenviron("~/.Renviron")
Sys.getenv("CENSUS_API_KEY")
```

```{r}
blocks<-c("Block Group 1, Census Tract 6112.05, Loudoun County, Virginia",
"Block Group 2, Census Tract 6112.05, Loudoun County, Virginia",
"Block Group 3, Census Tract 6112.05, Loudoun County, Virginia",
"Block Group 2, Census Tract 6112.04, Loudoun County, Virginia",
"Block Group 3, Census Tract 6112.04, Loudoun County, Virginia",
"Block Group 2, Census Tract 6115.02, Loudoun County, Virginia",
"Block Group 3, Census Tract 6115.02, Loudoun County, Virginia",
"Block Group 1, Census Tract 6113, Loudoun County, Virginia",
"Block Group 2, Census Tract 6113, Loudoun County, Virginia",
"Block Group 3, Census Tract 6113, Loudoun County, Virginia",
"Block Group 1, Census Tract 6114, Loudoun County, Virginia",
"Block Group 2, Census Tract 6114, Loudoun County, Virginia",
"Block Group 3, Census Tract 6114, Loudoun County, Virginia",
"Block Group 1, Census Tract 6117.01, Loudoun County, Virginia",
"Block Group 2, Census Tract 6117.01, Loudoun County, Virginia",
"Block Group 1, Census Tract 6116.02, Loudoun County, Virginia",
"Block Group 2, Census Tract 6116.02, Loudoun County, Virginia",
"Block Group 1, Census Tract 6116.01, Loudoun County, Virginia",
"Block Group 2, Census Tract 6116.01, Loudoun County, Virginia",
"Block Group 3, Census Tract 6112.02, Loudoun County, Virginia")

va20_2 <- get_acs(geography = "block group",
                  variables = c(hispanics = "B03002_012"),
                state = "VA",
                year = 2020,
                geometry = TRUE) %>%
filter(NAME %in% blocks)
```

```{r}

blocks_CDP<-c("Block Group 1, Census Tract 6112.05, Loudoun County, Virginia",
"Block Group 2, Census Tract 6112.05, Loudoun County, Virginia",
"Block Group 3, Census Tract 6112.05, Loudoun County, Virginia",
"Block Group 2, Census Tract 6112.04, Loudoun County, Virginia",
"Block Group 3, Census Tract 6112.04, Loudoun County, Virginia",
"Block Group 2, Census Tract 6115.02, Loudoun County, Virginia",
"Block Group 3, Census Tract 6115.02, Loudoun County, Virginia",
"Block Group 1, Census Tract 6113, Loudoun County, Virginia",
"Block Group 2, Census Tract 6113, Loudoun County, Virginia",
"Block Group 3, Census Tract 6113, Loudoun County, Virginia",
"Block Group 1, Census Tract 6114, Loudoun County, Virginia",
"Block Group 2, Census Tract 6114, Loudoun County, Virginia",
"Block Group 3, Census Tract 6114, Loudoun County, Virginia",
"Block Group 1, Census Tract 6117.01, Loudoun County, Virginia",
"Block Group 2, Census Tract 6117.01, Loudoun County, Virginia",
"Block Group 1, Census Tract 6116.02, Loudoun County, Virginia",
"Block Group 2, Census Tract 6116.02, Loudoun County, Virginia",
"Block Group 1, Census Tract 6116.01, Loudoun County, Virginia",
"Block Group 2, Census Tract 6116.01, Loudoun County, Virginia",
"Block Group 3, Census Tract 6112.02, Loudoun County, Virginia")

va_20_CDP <- va20_2 %>% filter (NAME %in% blocks_CDP)

```



```{r}

map <- read_excel("Sterling_Youth_Development.xlsx")
subset_map <- map[1:11,c(1,2:3)]

subset_map$Longitude <- as.numeric(subset_map$Longitude)
subset_map$Latitude <- as.numeric(subset_map$Latitude)


# Show first 20 rows from the `quakes` dataset
leaflet(data = subset_map) %>% addTiles() %>%
  addPolygons(data = va20_2,
color="yellow",
weight = 0.5,
smoothFactor = 0.2,
fillOpacity = 0.5) %>%
  addMarkers(~Longitude, ~Latitude, popup = ~as.character(Name), label = ~as.character(Name)) %>% addPolygons(data = va_20_CDP,
color="red",
weight = 0.5,
smoothFactor = 0.2,
fillOpacity = 0.5) %>%
  addMarkers(~Longitude, ~Latitude, popup = ~as.character(Name), label = ~as.character(Name)) 


# Plot it
#library(ggplot2)
#ggplot() +
  #geom_polygon(data = spdf_fortified, aes( x = long, y = lat, group = group), fill="#69b3a2", color="white") +
  #theme_void() 
```
```
    
    