---
title: "Median Income"
author: "Amanda E. Ljuba"
date: '2022-06-13'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
read_excel("incomemedian.xlsx")
medianin <- read_excel("incomemedian.xlsx")
```

```{r}
subset_medianin <- medianin[4:13, 1:5]
subset_medianin
mi_pop <- subset_medianin$...4
mi_cat <- subset_medianin$...1
```
,axis.text.y = element_blank()

```{r}
mi_cat.fac <- factor(mi_cat, levels = c(mi_cat))
subset_medianin$new_pop<-gsub("%$","",subset_medianin$...4)
pop_nop <- subset_medianin$new_pop
pop_num <- as.numeric(pop_nop)

ggplot(subset_medianin,aes(x=mi_cat.fac,y=pop_num, fill=mi_cat.fac))+geom_col(stat="identity")+theme(axis.text.x=element_blank(),axis.ticks.y=element_blank(),axis.title.x = element_blank()+scale_x_discrete(limits=mi_cat.fac),axis.text.y=element_blank())+labs(caption= "Source: S1901 ACS 5-year data 2016-2020",x="Income", y="Percent") + coord_polar() + guides(fill = guide_legend(title = "Income Level ($)"))
```
This shows the income of families in the past 12 months in the Sterling CPD using 2020 inflation adjusted dollars. The largest income level within the population of the Sterling CPD is the $100,000 to $149,999 bracket followed closely by both the %50,000 to $74,999 bracket and $150,000 to $199,999. The smallest income levels within the population of the Sterling CPD are the brackets less than $10,000 bracket to the  $35,000 to $49,999. Our data is skewed however because part of the Sterling CPD includes areas that are highly affluent as well as schools designated as Title 1